---
title: "Report2"
output: pdf_document
date: "2024-09-29"
editor_options: 
  markdown: 
    wrap: 72
---

# Abstract

This report analyzes the "Facebook Social Media Metrics" dataset to
provide detailed insights into the performance and engagement of
Facebook page posts over time. The dataset includes a wide range of
variables, such as the type of content posted (like photos, videos, and
status updates), the reach and impressions achieved, and the
interactions generated by each post, such as comments, likes, and
shares. By analyzing these metrics, we try to find factors that
influence audience behavior and engagement patterns on social media.

Hence, the primary focus of this report is on understanding the
relationship between Lifetime Post Consumers, as the response variable,
and Lifetime Engaged Users, as the covariate. Lifetime Post Consumers
refer to users who actively consume the content by clicking on links or
viewing embedded media, while Lifetime Engaged Users are those who
interact with the post, whether by liking, sharing, or commenting. These
two key variables can help us gauge engagement quality, determine what
type of content encourages passive consumption versus active engagement
and optimize content strategy. This report assists in determining the
relationship between these two variables to improve user engagement and
increase content consumption.

# Discussion and Conclusions

We have found evidence that there is a statistically significant
relationship between Lifetime Post Consumers and Lifetime Engaged Users.
The analysis of the relationship between Lifetime Engaged Users and
Lifetime Post Consumers reveals a strong positive correlation, as
indicated by both the scatterplot and the linear regression results. The
scatterplot shows that most data points closely align with the
regression line, highlighting a consistent linear trend between
engagement and content consumption. The positive correlation shows that
increased user engagement will result in higher number of consumption.
The R-squared value presents that the model fits the data well.

However, we also found a few outliers in the model. These outliers
indicate that while the model is a good fit overall, factors beyond user
engagement might influence post consumption in some cases, and
understanding these outliers could provide additional insights into
optimizing engagement strategies.

Overall, the linear model is effective for predicting post consumption
based on user engagement. Also, these findings provide valuable insights
for social media managers aiming to improve their content strategies and
enhance engagement metrics.

# Data Visualization

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2)
fb <- read.csv("Facebook_Project/dataset_Facebook.csv",
               sep = ";",
               header = TRUE,
               as.is = TRUE)
```

Response Variable (Y): Lifetime Post Consumers

Covariate (X): Lifetime Engaged Users

```{r}
data <- data.frame(
  Y = fb$Lifetime.Post.Consumers,
  X = fb$Lifetime.Engaged.Users
)
```

## Plotting Data

Scatterplot with Lifetime Post Consumers as the Y Axis and Lifetime
Engaged Users as the X Axis

```{r}
ggplot(data, aes(x=X, y=Y)) + 
  geom_point(size=0.15, col='blue') +
  theme_bw() +
  xlab("Lifetime Engaged Users") +
  ylab("Lifetime Post Consumers")
```

Interpretation: 

The scatterplot shows a general upward trend, indicating
a positive relationship between lifetime engaged users and lifetime post
consumers. Most of the data points lie close to a linear trend, though
there is one possible outlier below the linear trend with a high number
of lifetime engaged users and low lifetime post consumers. This positve
relationship suggests that engaging more users leads to a higher number
of post consumption.

# Linear Regression

OLS on Response Y (Lifetime Post Consumers) and Covariate X (Lifetime
Engaged Users)

```{r}
OLS <- lm(X ~ Y, data)
summary(OLS)
confint(OLS, level=0.95)
round(confint(OLS, level=0.95), digits=4)
vcov(OLS)
```

Interpretation: 

The regression results show a strong, positive, and
statistically significant relationship between "Lifetime Post Consumers"
and "Lifetime Engaged Users." The estimate of coefficient for "Y"
(Lifetime Post Consumers) is 1.08, confirming a positive relationship
between the number of post consumers and engaged users. The p-value for
both the intercept (0.00014) and the slope (\< 2e-16) are extremely
small, indicating that both coefficients are statistically significant
at a very high level (p \< 0.001). This implies that there is strong
evidence against the null hypothesis. The R-squared value of 0.9374
indicates that approximately 93.74% of the variability in "Lifetime Post
Consumers" can be explained by the "Lifetime Engaged Users." This high
R-squared value suggests a strong fit of the model to the data.


## Scatterplot with Regression Line

Overlay of The Linear Regression Fit on The Scatterplot

```{r}

intercept <- coef(OLS)[1]
slope <- coef(OLS)[2]
  
ggplot(data, aes(x=X, y=Y)) + 
  geom_point(size=0.15, col='blue') +
  theme_bw() +
  geom_abline(intercept = intercept, slope = slope, color = "red", lwd = 1.5) +
  xlab("Lifetime Engaged Users") +
  ylab("Lifetime Post Consumers")
```

Interpretation:

Overall, this linear regression model appears to be a good model for
explaining the relationship between "Lifetime Engaged Users" and
"Lifetime Post Consumers." The scatterplot with the overlay of the
regression line shows that most of the data points closely follow the
linear trend, further supporting the linear model's appropriateness.
There are a few outliers, especially at higher values, indicating that
while the linear model is generally a good fit, there may be some
deviation at the extremes.
